First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-08-21 eg6-letters/coherent/dvcs_he4_prl.tex
update the paper with the support statment in the acknowledgments
edit the acknowledgments
edit the Acknowledgments in the coherent paper

%Acknowledgments
The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional 
de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
U.S. Department of Energy, the UK Science and Technology Facilities Council 
(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
Research Foundation of Korea, and the Office of Research and Economic 
Development at Mississippi State University.  The author (M.~Hattawy) also 
acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem. The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.

>>>>

%Acknowledgments
The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional 
de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
U.S. Department of Energy under contract number DE-AC02-06CH11357, the UK Science and Technology Facilities Council (STFC), the Scottish Universities Physics Alliance (SUPA), the National Research Foundation of Korea, and the Office of Research and Economic 
Development at Mississippi State University. The author (M.~Hattawy) also 
acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem.  
The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.
